---
title: "p8105_hw1_zf2352"
author: "Zhenkun Fang"
date: "2024-09-21"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(tidyverse)
library(palmerpenguins)
```

```{r, include=FALSE}
data("penguins", package = "palmerpenguins")
```

# Problem 1

## Clean and look at the dataset
```{r problem1 - clean and look at the dataset}
penguins = janitor::clean_names(penguins)
penguins
nrow(penguins)
ncol(penguins)
```
This data set contains various variables of penguins：

- 'species': the specie of each penguin (Adelie, Chinstrap, Gentoo).

- 'island': the island where each penguin comes from (Biscoe, Dream, Torgersen).

- 'bill_length_mm': the bill length of each penguin in millimeters.

- 'bill_depth_mm': the bill depth of each penguin in millimeter.

- 'flipper_length_mm': the flipper length of each penguin in millimeters.

- 'body_mass_g': the body mass of each penguin in grams.

- 'sex': the biological sex of each penguin.

- 'year': the year of birth of each penguin (2007, 2008, 2009).

There are 344 rows and 8 columns in this dataset.

```{r problem1 - calculate mean flipper length}
mean(penguins$flipper_length_mm, na.rm = TRUE)
```

The mean flipper length is 200.9152 mm.

## Scatterplot
```{r problem1 - scatterplot, message = FALSE, warning = FALSE}
ggplot(
  penguins,
  aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + 
  geom_point() + 
  labs(
    title = "Bill length vs Flipper length",
    x = "bill length (mm)",
    y = "flipper length (mm))",
    color = "Penguin Species"
  )

ggsave("scatterplot_flipper_vs_bill.png")
```

# Problem 2

## Create data frame
```{r}
set.seed(1235)

normal_sample = rnorm(10)

logical_vector = normal_sample > 0

character_vector = sample(letters, 10)

factor_vector <- factor(sample(c("Level1", "Level2", "Level3"), 10, replace = TRUE))

df <- data.frame(Random_Sample = normal_sample,
                 Greater_Than_Zero = logical_vector,
                 Character_Vector = character_vector,
                 Factor_Vector = factor_vector)

print(df)
```
## Calculate mean
```{r, message = FALSE, warning = FALSE}
dbl_mean = mean(pull(df, Random_Sample)) %>% 
  print()
  
lgl_mean = mean(pull(df, Greater_Than_Zero)) %>% 
  print()

chr_mean = mean(pull(df, Character_Vector)) %>% 
  print()

fct_mean = mean(pull, Factor_Vector) %>% 
  print()
```
R can calculate the mean of random sample and logical vector (double and logical vectors).

```{r, eval = FALSE}
lgl_mean1 = mean(as.numeric(pull(df, Greater_Than_Zero))) %>% 
  print()

chr_mean1 = mean(as.numeric(pull(df, Character_Vector))) %>% 
  print()

fct_mean1 = mean(as.numeric(pull(df, Factor_Vector))) %>% 
  print()
```
R can calculate the mean of logical vector and factor vector. However, the mean of character vector cannot be calculated. 

logical vector: When converting a logical vector to numeric, TRUE becomes 1 and FALSE becomes 0.

character vector: When converting a character vector to numeric, R returns NA (missing values) because character data cannot be directly translated into numbers.

factor vector: When converting a factor to numeric, the factor levels are converted into integers representing their internal codes.

This helps explain what happens when I try to take the mean.
