---
title: "p8105_hw1_zf2352"
author: "Zhenkun Fang"
date: "2024-09-21"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(tidyverse)
library(palmerpenguins)
```

```{r}
data("penguins", package = "palmerpenguins")
```

## Problem 1

# Clean and look at the dataset
```{r problem1 - clean and look at the dataset}
penguins = janitor::clean_names(penguins)
penguins
nrow(penguins)
ncol(penguins)
```
This data set contains various variables of penguins：
- 'species': the specie of each penguin (Adelie, Chinstrap, Gentoo)
- 'island': the island where each penguin comes from (Biscoe, Dream, Torgersen)
- 'bill_length_mm': the bill length of each penguin in mm
- 'bill_depth_mm': the bill depth of each penguin in mm
- 'flipper_length_mm': the flipper length of each penguin in mm
- 'body_mass_g': the body mass of each penguin in gram
- 'sex': the biological sex of each penguin
- 'year': the year of birth of each penguin (2007, 2008, 2009)

There are 344 rows and 8 columns in this dataset.

```{r problem1 - calculate mean flipper length}
mean(penguins$flipper_length_mm, na.rm = TRUE)
```

The mean flipper length is 200.9152 mm.

# Scatterplot
```{r problem1 - scatterplot, message = FALSE, warning = FALSE}
ggplot(
  penguins,
  aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point() + 
  labs(
    title = "Bill length vs Flipper length",
    x = "bill length (mm)",
    y = "flipper length (mm))",
    color = "Penguin Species"
  )

ggsave("scatterplot_flipper_vs_bill.png")
```

## Problem 2


Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
